---
title: "Introduction To R using [R Markdown](http://rmarkdown.rstudio.com/) and [Bookdown](https://bookdown.org/yihui/bookdown/)"
author: "Your Name"
date: '`r format(Sys.time(), "%B %d, %Y at %X")`' 
bibliography: PackagesUsed.bib
output: 
  bookdown::html_document2: 
    highlight: textmate
    theme: yeti
---




**Directions:**  Recreate this document.  See Section \@ref(AG) for how to set up your YAML.   Make sure to commit and push both your `Lab1.Rmd` and resulting `Lab1.html` files to GitHub.  For more information on `knitr` [@R-knitr] code chunk options, see [https://yihui.name/knitr/options/](https://yihui.name/knitr/options/). Refer to [https://bookdown.org/yihui/bookdown/](https://bookdown.org/yihui/bookdown/) for information on labeling and referencing footnotes, sections, tables, equations, and figures. Use the following global options for your document:

````markdown
`r ''````{r, label = "SETUP", echo = FALSE, results= 'hide', message = FALSE, warning = FALSE}
knitr::opts_chunk$set(comment = NA, fig.align = 'center', fig.height = 5, fig.width = 5, 
                      prompt = FALSE, highlight = TRUE, tidy = FALSE, warning = FALSE, 
                      message = FALSE)
```
````


```{r, label = "SETUP", echo = FALSE, results= 'hide', message = FALSE, warning = FALSE}
knitr::opts_chunk$set(comment = NA, fig.align = 'center', fig.height = 5, fig.width = 5, 
                      prompt = FALSE, highlight = TRUE, tidy = FALSE, warning = FALSE, 
                      message = FALSE)
```

# Lab^[The material in Section \@ref(lab) is modified from the Chapter 2 lab of [_An introduction to Statistical Learning_](http://faculty.marshall.usc.edu/gareth-james/ISL/ISLR%20Seventh%20Printing.pdf).] {#lab} 


## Basic Commands

`R` uses functions to perform operations. To run a function called `funcname`, we type `funcname(input1, input2)`, where the inputs (or arguments) `input1` argument and `input2` tell `R` how to run the function. A function can have any number of inputs. For example, to create a vector of numbers, we use the function `c()` (for concatenate). Any numbers inside the parentheses are joined together.  The following command instructs `R` to join together the numbers 1, 3, 2, and 5, and to save them as a vector named `x`. When we type `x`, it gives us back the vector.

```{r}
x <- c(1, 3, 2, 5) 
x
```

Note that the `>` is not part of the command; rather, it is printed by `R` to  indicate that it is ready for another command to be entered. We can also save  things using `=` rather than `<-`:

```{r}
x = c(1, 6, 2)
x
y = c(1, 4, 3)
y
```

Hitting the _up_ arrow multiple times will display the previous commands, which can then be edited. This is useful since one often wishes to repeat a similar command. In addition, typing `?funcname` will always cause `R` to open a new help file window with additional information about the function `funcname`.

We can tell `R` to add two sets of numbers together. It will then add the first number from `x` to the first number from `y`, and so on. However, `x` and `y` should be the same length. We can check their length using the `length()` function.

```{r}
length(x)
length(y)
x + y
```

The `ls()` function allows us to look at a list of all of the objects, such as data and functions, that we have saved so far. The `rm()` function can be used to delete any that we don’t want.

```{r}
ls()
rm(x, y)
ls()
```

It’s also possible to remove all objects at once:

```{r}
rm(list = ls())
```

_____________

FILL IN THE MISSING TEXT AND CODE

____________

# Automagic Generation of `R` Package References {#AG}

Suppose the following `R` packages are used for a project: `DT`, `ggplot2`, `ISLR`, `knitr`, `plotly`, `dplyr`, `rmarkdown`, and `bookdown`.  

1. Create an object named `PackagesUsed`.
2. Write the packages used to a `*.bib` file.
3. Load the packages with `lapply()`. ^[Use `results = "hide"` in your code chunk to hide the results of `lapply()`.]
4. Add a `bibliography` entry to the YAML.
5. Cite the package using `@R-packagename` (look at the `*.bib` file for the exact name)
6. Add a `References` section header (`## References`) at the very end of the document.  The references will appear (provided they are cited) after the header.

```{r, results = "hide"}
PackagesUsed <- c("DT", "ggplot2", "ISLR", "knitr", "plotly", "dplyr", "rmarkdown", "bookdown")
# Write bib information
knitr::write_bib(PackagesUsed, file = "./PackagesUsed.bib")
# Load packages
lapply(PackagesUsed, library, character.only = TRUE)
```

Example YAML:

```{r, eval = FALSE}
---
title: "Introduction To R using [R Markdown](http://rmarkdown.rstudio.com/) and [bookdown](https://bookdown.org/yihui/bookdown/)"
author: "Your Name"
date: '`r format(Sys.time(), "%b %d, %Y")`'
bibliography: PackagesUsed.bib
output: 
  bookdown::html_document2: 
    highlight: textmate
    theme: yeti
---
```


This document uses `DT` by @R-DT, `ggplot2` by @R-ggplot2, `ISLR` by @R-ISLR, `plotly` by @R-plotly, `rmarkdown` by @R-rmarkdown, `dplyr` by @R-dplyr, `knitr` by @R-knitr, and `bookdown` by @R-bookdown.^[Use the appropriate syntax to cite your references.  Otherwise, your **References** will not be generated automatically.]  

The previous line with citations was created using:

```{r, eval = FALSE}
This document uses `DT` by @R-DT, `ggplot2` by @R-ggplot2, `ISLR` by @R-ISLR, `plotly` by @R-plotly, `rmarkdown` by @R-rmarkdown, `dplyr` by @R-dplyr, `knitr` by @R-knitr, and `bookdown` by @R-bookdown. 
```

```{r}
sessionInfo()
```

## References